paper

### 2024-01-23 Toronto_Victims_of_Crimes/outputs/paper/paper.qmd
Add prefer-html: true to utilize a function to upgrade table visualization

---
title: "paper"
author: "Chay Park"
date: today
format: pdf
editor: visual
bibliography: references.bib
---

@@

### Top-level finding, what is the one thing that we learn about the world because of this paper?

@@

# Pivot the data to have Assault, Sexual Violation, Robbery as columns
pivoted_table <- crime_subtype_table %>%
  pivot_wider(names_from = SUBTYPE, values_from = Victims_Count, values_fill = 0)

# Print the table using kable with additional styling
kable(pivoted_table, caption = "Total number of victims counted for each crime from the year 2014 to 2022", format = "html") %>%
  kable_styling(full_width = FALSE) %>%
  add_header_above(c(" ", "Victims Count" = 3))

@@

# Assuming 'pivoted_table2' is the table with Assault, Sexual Violation, Robbery columns from the above table code

# Create bar graphs for each crime subtype
bar_plot <- ggplot(pivoted_table2, aes(x = REPORT_YEAR)) +
  geom_bar(aes(y = Assault, fill = "Assault"), stat = "identity", position = "stack") +
  geom_bar(aes(y = `Sexual Violation`, fill = "Sexual Violation"), stat = "identity", position = "stack") +
  geom_bar(aes(y = Robbery, fill = "Robbery"), stat = "identity", position = "stack") +
  labs(x = "Year",
       y = "Number of Reported Victims of Crimes") +
  scale_fill_manual(values = c("Assault" = "grey", "Sexual Violation" = "brown", "Robbery" = "pink"),
                    name = "Crime Subtype") +
  theme_minimal() +
  scale_x_continuous(breaks = seq(2014, 2022, by = 1))

>>>>

---
title: "paper"
author: "Chay Park"
date: today
format: pdf
editor: visual
bibliography: references.bib
prefer-html: true
---

@@

### top-level finding, what is the one thing that we learn about the world because of this paper?

@@

# Pivot the data to have Assault, Sexual Violation, Robbery as columns
pivoted_table_2 <- crime_subtype_table %>%
  pivot_wider(names_from = SUBTYPE, values_from = Victims_Count, values_fill = 0)

# Print the table using kable with additional styling
kable(pivoted_table_2, caption = "Total number of victims counted for each crime from the year 2014 to 2022", format = "html") %>%
  kable_styling(full_width = FALSE) %>%
  add_header_above(c(" ", "Victims Count" = 3))

@@

# Assuming 'pivoted_table_2' is the table with Assault, Sexual Violation, Robbery columns from the above table code

# Create bar graphs for each crime subtype
bar_plot <- ggplot(pivoted_table_2, aes(x = REPORT_YEAR)) +
  geom_bar(aes(y = Assault, fill = "Assault"), stat = "identity", position = "stack") +
  geom_bar(aes(y = `Sexual Violation`, fill = "Sexual Violation"), stat = "identity", position = "stack") +
  geom_bar(aes(y = Robbery, fill = "Robbery"), stat = "identity", position = "stack") +
  labs(x = "Year",
       y = "Number of Reported Victims of Crimes") +
  scale_fill_manual(values = c("Assault" = "grey", "Sexual Violation" = "brown", "Robbery" = "pink"),
                    name = "Crime Subtype") +
  theme_minimal() +
  scale_x_continuous(breaks = seq(2014, 2022, by = 1))
